---
title: "Advanced Statistics Module 11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r comment=NA}
library(readxl)
df <- read.csv("C:/Users/adamw/Documents/Advanced Statistics/Datasets/Module 11 Data.csv", row.names=1)
df
```

First we import the data from an excel spreadsheet to a csv file named 'df' and conduct the chi-squared test.

```{r comment=NA}
chisq.test(df)
```

Here we see our critical values of the chi-squared test. We can see that the initial degrees of freedom are 4, and our p-value is .0598. Our null hypothesis in this case would be that whether someone is a beach-comer or a windsurfer has no effect on them choosing the same hotel again. Since we have a low p-value, there is evidence against this null hypothesis and we can infer that being a beach-comer or a windsurfer does in fact influence how likely one is to stay at the same hotel.

We can also take a look at other values of our chi-squared test such as the expected and residual numbers based off of our observed values in our dataset.

```{r comment=NA}
chitest = chisq.test(df)
chitest$expected
chitest$residuals
```


Next, we will graph the outcome of our chi-squared testing.

```{r comment=NA}
library("lattice")
densityplot(df$Beachcomber ~ df$Windsurfer, xlab = "Windsurfers")
densityplot(df$Windsurfer ~ df$Beachcomber, xlab = "Beach-comers")
```

These density graphs show the relationship between beach-comers and windsurfers and how likely they are to overlap at specific intervals.